FoRTE baseline

### 2019-03-25 analysis/paper/paper.Rmd
[paper] Add more discussion of ED submodels to intro

One realization of this is the Ecosystem Demography (v2) model [@moorcroft_2001_method; @medvigy_2011_predicting; @medvigy_2009_mechanistic].
This model has been used to simulate (examples...).

@@

Based on previous results [@fisher_2015_taking], we predict ED2 will over-predict dominance of early-successional canopy species (and under-predict understory productivity) under its default configuration.
Enabling dynamic N cycling and a finite canopy radius model will alleviate these issues, but will significantly increase the parameteric uncertainty due to strong sensitivity to N-cycling and canopy gap fraction parameters, respectively.
Constraining these parameters should be a high priority

@@

>>>>

One realization of this is the Ecosystem Demography (v2) model [@moorcroft_2001_method; @medvigy_2011_predicting; @medvigy_2009_mechanistic].
This model has been used to simulate (examples...).
Previous uncertainty analyses with ED:
[@dietze_2014_quantitative]...
More recently, [@raczka_2018_what]...

Light availability is a first order control on photosynthesis, and competition for light is a key process in driving competitive dynamics and community succession.
How light is distributed through a canopy is therefore critically important to accurately simulating community dynamics.
Radiative transfer models are used to simulate light proliferation through a canopy.
Detailed, 3D representations [@widlowski_2014_abstract; @widlowski_2007_third; @malenovsky_2008_influence] have prohibitively high computational costs for use in dynamic vegetation models.
Therefore, these models have had to rely on computationally-efficient approximations.
One common approach is the "two-stream approximation", originally developed for atmospheric radiative transfer [@meador_1980_two] and later adapted for plant canopies [@dickinson_1983_land; @sellers_1985_canopy].
<!-- TODO: Further discussion? -->
Although popular, the two-stream approach has some important limitations (REFS, details...).
An alternative approach is the "multiple scattering" model of @zhao_2005_multiple.
Accounting for multiple scattering enhances canopy light absorption, particularly in near-infrared wavelengths [@zhao_2005_multiple], therefore reducing the amount of light that makes it into the understory (TODO confirm).
<!-- TODO: Further discussion -->

Competition is also strongly determined by canopy structure and how it is represented (REF).
In other words, how much does canopy height matter compared to gappiness and horizontal competition?
C.f. [@hogan_2018_fast; @dietze_2008_changing].

Trait plasticity with light level also plays a role -- i.e. shaded leaves adapt to lower light levels.
C.f. [@keenan_2016_global; @lloyd_2010_optimisation; @niinemets_2016_within].

@@

Based on previous results [@fisher_2015_taking], we predict ED2 will over-predict dominance of early-successional canopy species (and under-predict understory productivity) under its default configuration.
Enabling dynamic N cycling and a finite canopy radius model will alleviate these issues, but will significantly increase the parameteric uncertainty due to strong sensitivity to N-cycling and canopy gap fraction parameters, respectively.
Constraining these parameters should be a high priority...

@@

## Future directions: Disturbance response modeling
